Social Visual Analytics: DevOps for Data Scientists

### 2015-03-25 introduction.tex
refine usership stats

Over the past two years, we prototyped this environment and deployed it
in a production community of data scientists, business analysts and other colleagues.
The platform today has over 200 active accounts, and several dozen people have forked
and customized code in the system. Most of the active users are members of
the statistics research department of our lab, but some others are data
scientists and other collaborators in business units. \stephen{I hope this is right.}

>>>>

Over the past two years, we prototyped this environment and deployed it in a
production community of data scientists, business analysts and other colleagues.
The platform today has over 300 active accounts; about 20 people use it more
than twice a week, and about 50 people use it more than once a week.  Most of
the active users are members of AT&T Labs, but some others are data scientists
and other collaborators in business units. \gordon{This doesn't measure how
intensely people use it...}
